What is an Ancestral Recombination Graph?

### 2022-03-01 paper.tex
Small update to EARG section

Fortunately, it is straightforward to generalise the classical Griffiths
encoding to both simplify implementations and to encompass any
possible pattern of genetic inheritance.
We require only two changes. Firstly, we let nodes in the
graph model \emph{genomes} rather than \emph{events}. As we
see in the next section, this allows us to model complex
patterns of inheritance without classifying different types of node.
The second change we must make is to associate
the details of inheritance intervals with \emph{edges} rather than
as breakpoints associated with recombination events and
edge ordering rules.
% That is, given two genomes $p$
% and $c$ where $p$ is the parent genome and $c$ is the child
% (although many generations may have elapsed between the two),
% we associate a set $I$ of intervals of genome which $c$ has
% inherited from $p$.
These changes are straightforward, involve no loss of information
and greatly increase both the expressivity and computational
power of ancestral recombination graph data structures.

>>>>

Fortunately, it is straightforward to generalise the classical Griffiths
EARG encoding to both simplify implementations and to encompass any
possible pattern of genetic inheritance.
The only change that we require is to associate
the details of inheritance intervals with \emph{edges} rather than
as breakpoints associated with recombination events and
edge ordering rules. This is illustrated in Fig~\ref{fig-arg-data-structure}B
where this alternative edge annotation formulation is
shown. By associating the interval $(0, x)$ with edge $(3,4)$
and the interval $(x, L)$ with $(3, 5)$ we make the encoding
unambigous: we can list the edges in any order, and it
will describe the same set of local genealogical trees.
This approach is also more flexible, because any pattern
of inheritance can be described by these intervals. For
example, if a gene conversion event occured where a segment
between between positions $x$ and $y$ was inherited by
node $3$ from $5$, we would state this by associating
the intervals $\{(0, x], (y, L]\}$ with $(3,4)$ and
$\{(x, y]\}$ with $(3,5)$.
This change is straightforward, involves no loss of information
and (as we see in later sections)
greatly increases both the expressivity and computational
power of ancestral recombination graph data structures.
